fabl: Fast Beta Linkage

### 2021-06-04 notes/fabl_wss.Rmd
wss second draft

- Comparisons for each field $f$ are binned to integers $\{1, \ldots, L_f\}$, with 1 being the highest level of agreement
  - Common to use $\{1, 2\}$ to reflect exact agreement or disagreement, and $\{1, 2, 3\}$ to allow for partial agreement

@@

$$P(\Gamma|\mathbf{Z}, \mathbf{m}, \mathbf{u}, \lambda) =\prod_{j=1}^{n_B}  \prod_{i=1}^{n_A}\mathbf{m}_{ij}^{\mathbf{1}_{z_j = i}}\mathbf{u}_{ij}^{\mathbf{1}_{z_j \neq i}}$$

$$\mathbf{m^{f}} \sim \text{Dirichlet}(\alpha^{f1}, \ldots, \alpha^{fL_f})$$
$$\mathbf{u^{f}} \sim \text{Dirichlet}(\beta^{f1}, \ldots, \beta^{fL_f})$$
$$Z_j | \lambda =
\begin{cases} 
    \frac{1}{n_A}\lambda  & z_j \leq n_A; \\
     1-\lambda &  z_j  = n_A + 1 \\
\end{cases}$$

$$\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda}) $$

>>>>

- Comparisons for each field $f$ are binned to integers $\{1, \ldots, L_f\}$, with 1 being the highest level of agreement

  - Common to use $\{1, 2\}$ to reflect exact agreement or disagreement, and $\{1, 2, 3\}$ to allow for partial agreement

@@

$$P(\Gamma|\mathbf{Z}, \mathbf{m}, \mathbf{u}, \lambda) =\prod_{j=1}^{n_B}  \prod_{i=1}^{n_A}\mathbf{m}_{ij}^{\mathbf{1}_{z_j = i}}\mathbf{u}_{ij}^{\mathbf{1}_{z_j \neq i}}$$
$$\mathbf{m^{f}} \sim \text{Dirichlet}(\alpha^{f1}, \ldots, \alpha^{fL_f})$$
$$\mathbf{u^{f}} \sim \text{Dirichlet}(\beta^{f1}, \ldots, \beta^{fL_f})$$
$$Z_j | \lambda =
\begin{cases} 
    \frac{1}{n_A}\lambda  & z_j \leq n_A; \\
     1-\lambda &  z_j  = n_A + 1 \\
\end{cases}$$
$$\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda}) $$
